Activity Monitoring - Quantified Self
===========================================================

Some context


This piece of code will read the data from your working directory:

```{r readdata}
act <- read.csv(unz("./RepData_PeerAssessment1/activity.zip", "activity.csv"))
act<-transform(act,interval = as.factor(interval))
act<-transform(act,date = as.factor(date))
library(ggplot2)
library(plyr)
```

Now for the frequency bit:

```{r Meanandhistogram}
stepsum<-tapply(act$steps,act$date,sum,na.rm=TRUE)
hist(stepsum)
hist(stepsum, breaks=30, xlab = "Step Count", main ="Step count by day")
stepferq<- mean(stepsum)
stepmedian<-median(stepsum)
```




```{r avgdailyactivitypattern}
Temp<-tapply(activity$steps,activity$interval,mean,na.rm=TRUE)
data<-as.data.frame(cbind(as.numeric(as.character(levels(activity$interval))),Temp))
ggplot(data, aes(V1, Temp)) + geom_line()+xlab("Interval")+ ylab("Number of steps")
Maxinterval<-data$V1[data$Temp==max(data$Temp)]
```

act1<-ddply(act,'interval',transform, stepbyint= mean(steps))
```{r navalues}
activity2<-activity
countna<-sum(as.numeric(is.na(activity2$steps)))
activity2$steps[is.na(activity2$steps)==TRUE]<-1
stepsum2<-tapply(activity2$steps,activity2$date,sum)
stepferq2<- mean(stepsum2)
stepmedian2<-median(stepsum2)
```


```{r panelgraphs}
activity2$date<-strptime(activity2$date, format ="%Y-%m-%d", tz="GMT")
activity2$Weekday<- "Weekday"
activity2$Weekday[weekdays(activity2$date)=="Sunday"|weekdays(activity2$date)=="Saturday"]<-"Weekend" 

